The paper on \Large \bf Blockchain Frontrunning

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] minor fixes. still 19 pages :barber:

The concept of the \emph{front-running} is decades old starting with early financial markets. Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change. Clearly, in such scenarios front-running was possible yet not detectable as a damaging activity. However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, a new form of front-running is feasible through high-speed networks. Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}. Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis. Surprisingly, there was no ICO (initial coin offering) included in the top 25 Dapps list by the time we fetched the data from the website. We believe the reason is that the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over. Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 Dapps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}

@@

As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \texttt{DAppradar.com}\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} in the first week of September 2018. We then categorize these applications into 4 principal groups of decentral applications (see Table~\ref{tab:top25dapps}). In this section, we take a deep look into one or two decentral applications from each category and pinpoint the technical details of front-running issue on each case. Although no ICOs were spotted on the list at the time it was retrieved, we will thoroughly discuss our analysis of how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).

@@

There have been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}. On our DApp samples, there was not ICOs mainly because they tend to run for a short time with a high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppradar.com}. Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these type of DApps. %ICOs due to the defined cap is similar to our analogy of a queue line, people would line up to get in and there's an opportunity to front-run. 
Here we focus on one ICO that our preliminary research showed that there might have been a front-running incident. There is no doubt that similar behaviour could be seen in other instances of ICOs or similar DApps if investigated.

@@

In the traditional markets, front-running is considered unethical and illegal. In the blockchain space, the designers of the decentral applications cannot rely on the justice system for preventing unethical behavior, and they must assume that each participant in the network acts rationally in their own self interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books. The methods discussed within these projects prevent blockchain network participants from front-running the orders as the orders are private and not known to the network and will not be broadcasted. However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.

\emph{Traditional Front-running Prevention Methods}. There are debates in traditional markets regarding the fact that front-running is considered to be a form of insider trading which deemed to be illegal. Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}. As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however front-running became less likely to happen mainly because of the high fine and law suits against firms whom behaved in an unethical way. Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in variety of regulated trading systems.

The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors whom are front-running could be anonymous and the fear of lawsuits would not apply. \\

@@

\subsubsection{Design Decision \#2:Privacy Preserving Blockchain\newline}
Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs. Privacy is a basic human right, that being said, there are limitations with the functionality of a system designed to preserve full privacy. However other than past transactions, real time transactions would leak informations about the sender or the intention of the order that could lead to front-running attacks. Privacy preserving blockchains try to solve the initial issue by keeping all the details of the transactions private (in some extent~\cite{miller2017empirical, kappos2018empirical}). 
As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses. Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data. However shielded addresses are private and do not leak any information, this is great for privacy but not good for smart contracts capabilities. Smart contract functionality requires verification by the miners which require to know the input, functionality and output of smart contracts to be able to determine if the transaction is valid. Albeit by using cryptographic primitives such as zero-knowledge proofs this issue could also be resolved~\cite{kosba2016hawk}.

\subsubsection{Design Decision \#3: Dual Authoring\newline} % S 2 M: this is still vague, it requires better explanation.
Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}. This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain. To achieve high liquidity and price improvement, Loopring orders are grouped in \emph{ring orders}. After the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement. While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key. By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}. However, in the new version of Loopring protocol this issue is resolves using the \emph{dual-authoring} scheme. This solution sets two levels of authorization for orders - one for settlement, and one for order matching. As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of any order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key. These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}. The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction. Doing so, it is assured that (i) the orders are not modified (because they are signed by the owner), (ii) no other miner can mine the ring (because the miner's address is signed by the initial miner), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).

@@

\subsubsection{Design Decision \#1: Commitment Scheme\newline} \label{CommitmentScheme}
Commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}. Commitment scheme is a robust method to prevent information leakage from the sensitive transactions. This could be done by simply submiting the hash value of the committed data to a smart contract and later on revealing the values linked to the committed hash, see Figure~\ref{fig:commitReveal}. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. This method is not perfect, depending on the DApp design, either the order is collateralized, that means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be vulnerable to Denial-of-Service attacks. 
Another use of such commitment scheme, is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS). In this case, a user sends a commit transaction, which commits to the name hash, similar to a sealed bid. Once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running. Similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however their participation and weight of the vote are publicly known. 
Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible there after. Also this scheme means two transaction are required for a functionality which is makes it more expensive to run.

@@

\subsubsection{Design Decision \#2: Submarine Commitments\newline}\label{submarineCommits}
Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized. With submarine send, it is possible to hide sender, receiver, value and data, the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.

The details of how Submarine commitments work is outside the scope of this paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address of which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}. However, this could be design in other ways to suit the need of the DApp. Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.

@@

\subsubsection{Design Decision \#3: Logic Specific Solutions\newline}
There is no perfect generic solution to this issue as of now, however to prevent front-running, one can design the application in a way that it is not possible to be front-run:

\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed not to rely on the time for the orders to be executed. For example when designing a decentral exchange, one can use \emph{the call market} design instead of a time-sensitive order book. In a call market design, the arrival time of the orders do not matter as they are executed in batches~\cite{clark2014decentralizing}.

@@

Going back to Table~\ref{tab:top25dapps}, some DApps facilitate different methods to mitigate front-running issues. As an example LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See ~\ref{code:localethereum}), hence removing any possibility of replay attack or possibility of any other address sending the similar order.

%Possibly remove this code snippet due to page limit
\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract. Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum},float]
    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
        payable external {
        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
	...
        // A signature (v, r and s) must come from localethereum to open an escrow
        bytes32 _invitationHash = keccak256(abi.encodePacked(
            _tradeHash,
            _paymentWindowInSeconds,
            _expiry
        )); 
\end{lstlisting}

>>>>

The concept of the \emph{front-running} is decades old starting with early financial markets. Initially, the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change. Clearly, in such scenarios front-running was possible yet not detectable as a damaging activity. However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore, a new form of front-running is feasible through high-speed networks. Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}. Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} Using this criteria, we successfully categorized these decentral applications into 4 principal categories on which we conduct our analysis. Surprisingly, there was no ICO (initial coin offering) included in the top 25 DApps list by the time we fetched the data from the website. We believe the reason is that the ICOs are inherently different from other groups of Daaps as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over. Therefore, we  consider ICOs as other cases on which the front-running should be investigated (although they are not listed in the top 25 DApps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}

@@

As mentioned in the Section~\ref{sec:intro}, for the purpose of this research we retrieved the top 25 DApps based on recent user activities from \texttt{DAppradar.com}\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} in the first week of September 2018. We then categorize these applications into 4 principal groups of decentral applications (see Table~\ref{tab:top25DApps}). In this section, we take a deep look into one or two decentral applications from each category and pinpoint the technical details of front-running issue on each case. Although no ICOs were spotted on the list at the time it was retrieved, we will thoroughly discuss our analysis of how ICOs are highly vulnerable to front-running activities (see Section~\ref{sec:ICOsfrontrunning}).

@@

There have been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}. On our DApp samples, there was not ICOs mainly because they tend to run for a short time with a high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppRadar.com}. Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these type of DApps. %ICOs due to the defined cap is similar to our analogy of a queue line, people would line up to get in and there's an opportunity to front-run. 
Here we focus on one ICO that our preliminary research showed that there might have been a front-running incident. There is no doubt that similar behaviour could be seen in other instances of ICOs or similar DApps if investigated.

@@

In the traditional markets, front-running is considered unethical and illegal. In the blockchain space, the designers of the decentral applications cannot rely on the justice system for preventing unethical behavior, and they must assume that each participant in the network acts rationally in their own self-interest, the application will be operating in an adversarial environment~\cite{0xfrontrunning:online}.
A few decentral exchange projects such as \textit{EtherDelta} and \textit{0xProject}~\cite{warren20170x}, have proposed solutions for front-running, which is off-chain order books. The methods discussed within these projects prevent blockchain network participants from front-running the orders as the orders are private and not known to the network and will not be broadcasted. However they are introducing third parties, \eg relayers in 0xproject, to be managing the orders with the promise not to reorder or front-run other orders.

\emph{Traditional Front-running Prevention Methods}. There are debates in traditional markets regarding the fact that front-running is considered to be a form of insider trading which deemed to be illegal. Traditional methods to prevent front-running mainly involves after the fact investigation and legal action against the front-runners~\cite{LexisNexisLawSuit}. As mentioned in section~\ref{traditionalFrontrunning}, defining front-running and educating the employees were the first step taken to prevent such issues in traditional markets, however, front-running became less likely to happen mainly because of the high fine and lawsuits against firms who behaved in an unethical way. Other methods such as dark pools~\cite{zhu2014dark, buti2011diving} and sealed bids~\cite{radner1989sealed} were discussed and implemented in a variety of regulated trading systems.

The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors who are front-running could be anonymous and the fear of lawsuits would not apply. \\

@@

\subsubsection{Design Decision \#2:Privacy-Preserving Blockchain\newline}
Market participants are concerned about revealing information on their past trades, purchases, income, or liquidity needs. Privacy is a basic human right, that being said, there are limitations to the functionality of a system designed to preserve full privacy. However other than past transactions, real-time transactions would leak information about the sender or the intention of the order that could lead to front-running attacks. Privacy-preserving blockchains try to solve the initial issue by keeping all the details of the transactions private (in some extent~\cite{miller2017empirical, kappos2018empirical}). 
As an example, ZCash~\cite{hopwood2016zcash}, uses two distinct type of addresses, transparent addresses and shielded addresses. Transparent addresses work similar to Bitcoin transactions, fully transparent about the sender and receiver addresses, the amount and included data. However shielded addresses are private and do not leak any information, this is great for privacy but not good for smart contracts capabilities. Smart contract functionality requires verification by the miners which require to know the input, functionality, and output of smart contracts to be able to determine if the transaction is valid. Albeit by using cryptographic primitives such as zero-knowledge proofs this issue could also be resolved~\cite{kosba2016hawk}.

\subsubsection{Design Decision \#3: Dual Authoring\newline} % S 2 M: this is still vague, it requires better explanation.
Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}. This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain. To achieve high liquidity and price improvement, Loopring orders are grouped in \emph{ring orders}. After the required signatures are provided by a miner and owner of the order, see Figure~\ref{fig:vulnerable_loopring}, the ring miner sends the \emph{submitRing transaction} to the Loopring Smart Contract (LPSC) for verification and settlement. While the \emph{submitRing transaction} sits unconfirmed in the mempool, any front-runner can create a copy of this transaction with his address instead of the ring miner's address and then sign the hash of the ring using his own private key. By paying a higher gasPrice, block miners choose the front-runner's transaction instead of the original \emph{submitRing transaction}. However, in the new version of Loopring protocol, this issue is resolves using the \emph{dual-authoring} scheme. This solution sets two levels of authorization for orders - one for settlement, and one for order matching. As it can be seen in Figure~\ref{fig:not_vulnerable_loopring}, each owner of an order generates a pair of public key (auth-address) and private key (auth-key), which are different from his address and its corresponding private key. These auth-keys are used to sign the hash of the ring and will further prevent anyone from regenerating the same \emph{submitRing transaction}. The reason is that the auth-keys are only known to the miner of the ring as they are not part of the on-chain transaction. Doing so, it is assured that (i) the orders are not modified (because they are signed by the owner), (ii) no other miner can mine the ring (because the miner's address is signed by the initial miner), and no user can front-run the \emph{submitRing transaction} (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).

@@

\subsubsection{Design Decision \#1: Commitment Scheme\newline} \label{CommitmentScheme}
The commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}. The commitment scheme is a robust method to prevent information leakage from the sensitive transactions. This could be done by simply submitting the hash value of the committed data to a smart contract and later on revealing the values linked to the committed hash, see Figure~\ref{fig:commitReveal}. 
In the case of decentral exchanges, the user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, the user sends reveal transaction revealing the order details which will be executed in a fair order. This method is not perfect, depending on the DApp design, either the order is collateralized, that means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be vulnerable to Denial-of-Service attacks. 
Another use of such a commitment scheme is in decentralized naming systems, such as Namecoin, Ethereum Name Service (ENS). In this case, a user sends a commit transaction, which commits to the name hash, similar to a sealed bid. Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running. A similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known. 
Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In the ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible thereafter. Also, this scheme means two transactions are required for a functionality which makes it more expensive to run.

@@

\subsubsection{Design Decision \#2: Submarine Commitments\newline}\label{submarineCommits}
Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} are similar to the commitment schemes with some key differences such as hiding participatory factor and being fully collateralized. With submarine send, it is possible to hide sender, receiver, value, and data, the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants.

The details of how Submarine commitments work is outside the scope of this paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address of which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}. However, this could be designed in other ways to suit the need of the DApp. Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.

@@

\subsubsection{Design Decision \#3: Logic Specific Solutions\newline}
There is no perfect generic solution to this issue as of now, however, to prevent front-running, one can design the application in a way that it is not possible to be front-run:

\noindent\emph{Eliminating Time-Order Dependency:} The applications can be designed not to rely on the time for the orders to be executed. For example when designing a decentral exchange, one can use \emph{the call market} design instead of a time-sensitive order book. In a call market design, the arrival time of the orders does not matter as they are executed in batches~\cite{clark2014decentralizing}.

@@

Going back to Table~\ref{tab:top25DApps}, some DApps facilitate different methods to mitigate front-running issues. As an example, LocalEthereum, an escrow-based exchange, uses challenge random values from the website to be included in the signature of the transaction (See ~\ref{code:localethereum}), hence removing any possibility of replay attack or the possibility of any other address sending the similar order.

%Possibly remove this code snippet due to page limit . don't forget to remove the refrence to it ^
\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract. Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum},float]
    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
        payable external {
        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
	...
        // A signature (v, r and s) must come from localethereum to open an escrow
        bytes32 _invitationHash = keccak256(abi.encodePacked(
            _tradeHash,
            _paymentWindowInSeconds,
            _expiry
        )); 
\end{lstlisting}

### 2018-09-17 frontrunning/Latex/setup/table.tex
[frontrunning] minor fixes. still 19 pages :barber:

\end{tabular}
\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com} on September 4th, 2018. Dapps that are represented in Italic format are analyzied and discussed in this paper.}\label{tab:top25dapps}}
\end{table}

>>>>

\end{tabular}
\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{DAppRadar.com} on September 4th, 2018. DApps that are represented in Italic format are analyzied and discussed in this paper.}\label{tab:top25DApps}}
\end{table}
